The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-07-03 analysis/paper/paper.qmd
Update usage of ngram column names

## Add lemmas as optional column to ngram function

@@

spacyr::spacy_parse(emu_theses_bigrams$first)

bigram_counts <- emu_theses_bigrams |> 
  count(first, second, sort = TRUE)

bigram_stem_counts <- emu_theses_bigrams |> 
  count(first_stem, second_stem, sort = TRUE)

@@

trigram_counts <- emu_theses_trigrams |> 
  count(first, second, third, sort = TRUE)

>>>>

@@

spacyr::spacy_parse(emu_theses_bigrams$w_1)

bigram_counts <- emu_theses_bigrams |> 
  count(w_1, w_2, sort = TRUE)

bigram_stem_counts <- emu_theses_bigrams |> 
  count(w_1_stem, w_2_stem, sort = TRUE)

@@

trigram_counts <- emu_theses_trigrams |> 
  count(w_1, w_2, w_3, sort = TRUE)
